---
name: Michael J.
surname: Carter
position: "Assistant Professor | Sensorimotor Control & Learning"
address: "Department of Kinesiology, Faculty of Science, McMaster University"
phone: +1 905 525 9140 x20391
www: www.cartermaclab.org
email: "michaecarter@mcmaster.ca"
twitter: cartermaclab
github: cartermaclab
orcid: 0000-0002-0675-4271
date: "Last update: `r format(Sys.time(), '%B %Y')`"
#headcolor: ffa300 #orange
#headcolor: 6acad8 #blue
headcolor: 414141
output: vitae::awesomecv
always_allow_html: yes
header-includes:
  \usepackage{longtable}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
library(emojifont)
library(fontawesome)
library(kableExtra)
library(huxtable)
```

# Research Interests

Decision-making for action; Joint action (Human-Human and Human-Robot); Feedback; Aging; Metascience

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Centre for Neuroscience Studies, Queen's University", "2016-17", "Postdoctoral Fellowship", "Kingston ON, Canada",
  "School of Human Kinetics, University of Ottawa", "2011-16", "Ph.D in Human Kinetics", "Ottawa ON, Canada",
  "Department of Physical Education & Kinesiology, Brock University", "2008-11", "M.Sc. in Kinesiology", "St. Catharines ON, Canada",
  "Department of Physical Education & Kinesiology, Brock University", "2004-08", "B.Ph.Ed (Honours)", "St. Catharines ON, Canada",
) %>% 
  detailed_entries(Degree, Year, Institution, Where,)
```

# Professional Organizations

Canadian Society for Psychomotor Learning & Sport Psychology (SCAPPS); Society for Transparency, Openness, & Replication in Kinesiology (STORK); Society for the Neural Control of Movement (NCM); North American Society for the Psychology of Sport & Physical Activity (NASPSPA)

# Employment History

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Department of Kinesiology, McMaster University", "2017-Present", "Assistant Professor", "Hamilton ON, Canada",
  "Centre for Neuroscience Studies, Queen's University", "2016-17", "Postdoctoral Fellow", "Kingston ON, Canada",
  "School of Kinesiology and Health Studies, Queen's University", "2016-17", "Teaching Adjunct Professor", "Kingston ON, Canada",
  "School of Human Kinetics, University of Ottawa", "2012-16", "Part-time Professor", "Ottawa ON, Canada",
) %>% 
  detailed_entries(Degree, Year, Institution, Where,)
```

# Trainees

## Masters

```{r}
tibble(
  Years = c(rep("2019-21", 2)),
  Name = c("*Mirette Mounir (SSHRC CGS-M)", "*Rajbir Sidhu (NSERC CGS-M)"),
  Program = c(rep("Kinesiology", 2)),
  Status = c(rep("Completed", 2)),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny *Denotes trainee holds external funding",
    escape = F
  ) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 1, width = '1.5cm') %>%
  column_spec(column = 2, width = '5cm') %>% 
  column_spec(column = 3:4, width = "3cm")
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

## Doctoral

```{r}
tibble(
  Years = c(rep("2018-", 2)),
  Name = c("*Laura St. Germain (NSERC PGS-D)", "Kyung-Hyun (Ruth) Kim"),
  Program = c("Kinesiology", "Psychology"),
  Status = c(rep("In Progress", 1), "In Progress - On maternity leave until Aug 2022"),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny *Denotes trainee holds external funding",
    escape = F
  ) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 1, width = '1.5cm') %>%
  column_spec(column = 2, width = '5cm') %>% 
  column_spec(column = 3, width = "2cm") %>% 
  column_spec(column = 4, width = "7.5cm")
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

# Lifetime Research Funding

## Current

[4]. 2018-23, **Carter MJ**. *Establishment of the Memory Action, & Cognition laboratory for the study of human sensorimotor neuroscience*. Ontario Research Fund-Research Infrastructure, $127,514 total over 5 years.

[3]. 2018-23, **Carter MJ**. *Establishment of the Memory Action, & Cognition laboratory for the study of human sensorimotor neuroscience*. Canadian Foundation for Innovation John R. Evans Leaders Fund, $127,514 total over 5 years.

[2]. 2018-2023, **Carter MJ**. *Decision-making and assignment policies in sensorimotor neuroscience*. Natural Sciences & Engineering Research Council of Canada Discovery Grant, $149,000 total over 5 years.

[1]. 2017, **Carter MJ**. Research startup funds from McMaster University, $1000,000 total (no expiry date).

<!-- &nbsp; -->

## Previous

[1]. 2018-19, **Carter MJ**. *Decision-making and assignment policies in sensorimotor neuroscience*. Natural Sciences & Engineering Research Council of Canada Discovery Launch Supplement Early Career Researcher, $12,500 total over 1 year.

# Honours, Awards, Scholarships

<!-- 2016, Dean’s Award, University of Ottawa, $3000. -->

<!-- 2015, Michael Smith Foreign Study Supplement, Natural Sciences & Engineering Research Council of Canada, $6000. -->

2014, Franklin Henry Young Scientist Award (Motor Control and Learning), *Canadian Society for Psychomotor Learning & Sport Psychology*.

<!-- 2013-15, Alexander Graham Bell Canada Graduate Scholarship (Doctoral), Natural Sciences & Engineering Research Council of Canada, $70,000. -->

<!-- 2009-10, Frederick Banting and Charles Best Canada Graduate Scholarship (Masters), Canadian Institutes of Health Research, $17,500. -->

<!-- 2009-10, Ontario Graduate Scholarship (Masters), Province of Ontario, $15,000 - [Declined] -->

<!-- 2008, Undergraduate Student Research Award, Brock University, $3250 -->

<!-- 2008, Graduated with First-Class Standing, Brock University -->

# Scholarly and Professional Activities

## Grant, scholarship & award committees

```{r}
tibble(
  Years = c("2019", "2019", "2012-13"),
  Role = c(rep("Reviewer", 3)),
  Name = c("Canadian Society for Psychomotor Learning and Sport Psychology Franklin
Henry Young Scientist Award", "Ontario Women’s Health Scholarship", "University of Ottawa Faculty of Health Sciences Research Funding"),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 3, width = '15cm')
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

## Ad hoc journal referee

Biological Psychology; Canadian Journal of Experimental Psychology; Clinical Neurophysiology; Experimental Brain Research; Human Movement Science; Journal of Learning & Instruction; Journal of Motor Behavior; Journal of Motor Learning & Development; Journal of Sport Sciences; Perceptual & Motor Skills; Psychological Research; Psychology of Sport & Exercise; Research Quarterly for Exercise & Sport

## External grant reviews
```{r}
tibble(
  Years = c("2021-22", "2019-20"),
  Role = rep("Reviewer", 2),
  Name = rep("Natural Sciences and Engineering Research Council of Canada Discovery
Grant Competition, Biological Systems and Functions", 2),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 3, width = '15cm')
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

# Teaching

## Undergraduate
```{r}
tibble(
  Years = c("2022-Present", "2018-Present", "2016-17", "2015-16", "2012-16"),
  Institution = c(rep("McMaster University", 2), "Queen's University", rep("University of Ottawa", 2)),
  Course = c("Human Robotics", "Motor Control and Learning", "Motor Learning and Control", "Psychomotor Behaviour Lab", "Motor Control and Learning"),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 3, width = '15cm')
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

## Graduate
```{r}
tibble(
  Years = c(rep("2018-Present", 2)),
  Institution = c(rep("McMaster University", 2)),
  Course = c("Statistical Methods in Kinesiology", "Motor Control"),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 3, width = '15cm')
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

# Supervisory committees

## Masters

```{r}
tibble(
  Years = c("2020-", rep("2019-21", 2), "2018-21", rep("2018-20", 2), rep("2017-19", 4)),
  Name = c("Karishma Ramdeo", "Kristen DeMelo", "Noah Erskine", "Patrick Dans", "Ashley Flemington", "Jacqueline Brillantes", "Mitchell Locke", "Stephen Toepp", "Stevie Foglia", "Kumara Somasundram"),
  Program = c(rep("Kinesiology", 10)),
  Status = c(rep("In Progress", 1), rep("Completed", 9)),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 1, width = '1.5cm') #%>%
  #column_spec(column = 2:4, width = "3.5cm")
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

## Doctoral

```{r}
tibble(
  Years = c("2019-", rep("2018-", 2), "2017-19"),
  Name = c("Stephen Toepp", "Chantal Carillo", "Claire Tuckey", "Jessica Cappelletto"),
  Program = c("Kinesiology", "Psychology", rep("Kinesiology", 2)),
  Status = c(rep("In Progress", 3), "Completed"),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 1, width = '1.5cm') #%>%
  #column_spec(column = 2:4, width = "3.5cm")
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

# Examination Committees

## External examiner
```{r}
tibble(
  Year = c("2020", rep("2018", 3), rep("2017", 2)),
  Name = c("Molly Brillanger", "Stephanie Reischel", "Jenin El-Sayes", "Lana Pfaff", "Claire Tuckey", "Hunter Fassett"),
  Degree = c(rep("M.Sc", 6)),
  Program = c(rep("Kinesiology", 6)),
  Institution = c(rep("Brock University", 2), "McMaster University", "Laurier University", "Brock University", "McMaster University"),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 1, width = '1.5cm') #%>%
  #column_spec(column = 2:4, width = "3.5cm")
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

## Internal examiner
```{r}
tibble(
  Year = "2018",
  Name = "Denver Brown",
  Degree = "Ph.D",
  Program = "Kinesiology",
  Institution = "McMaster University",
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 1, width = '1.5cm') #%>%
  #column_spec(column = 2:4, width = "3.5cm")
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

## Comprehensive examiner
```{r}
tibble(
  Year = c("2020", "2019"),
  Name = c("Chantal Carillo", "Claudia Turco"),
  Degree = c(rep("Ph.D", 2)),
  Program = c("Psychology", "Kinesiology"),
  Institution = c(rep("McMaster University", 2)),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 1, width = '1.5cm') #%>%
  #column_spec(column = 2:4, width = "3.5cm")
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

# Undergraduate Supervision

## Research assistants
```{r}
tibble(
  Year = c("2021", "2020", "2019"),
  Name = c("Elizabeth Mitchell", "*Allison Williams", "*Andrew Poskus"),
  Program = c("Integrated Biomedical Engineering \\& Health Sciences", rep("Kinesiology", 2)),
  Institution = c(rep("McMaster University", 3)),
  Type = c("Co-op", rep("NSERC USRA", 2)),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny *Denotes external funding",
    escape = F
  ) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 1, width = '1.5cm')
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

## Research practicums

```{r}
tibble(
  Year = c(rep("2022", 2), rep("2021", 6), rep("2020", 3), rep("2019", 4), rep("2018", 4)),
  Name = c("Vivian Li", "Caroline Jarvi", "Gurlal Gill", "Anita Chaseendran", "Gianna Jeyarajan", "Kenzie Bell", "Ashton Yuen", "Charlie Violin", "Ammaar Jan", "Faran Chaudhry", "Yu (Sarah) Fu", " Andrew Poskus", "Maya El-Zahed", "Grant Yang", "Olena Leshchyshen", "Rita Waseem", "Christian Kleiser", "Chris Li", "Faryal Zahir"),
  Program = c("Engineering", "Life Sciences", "Kinesiology", rep("Life Sciences", 2), rep("Kinesiology", 4), rep("Health Sciences", 2), rep("Kinesiology", 4), "Life Sciences", rep("Kinesiology", 2), "Biology"),
  Level = c(rep("III", 4), "IV", rep("III", 3), rep("IV", 2), rep("III", 8), "IV"),
  Institution = c(rep("McMaster University", 19)),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 1, width = '1.5cm') #%>%
  #column_spec(column = 2:4, width = "3.5cm")
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

## Honours thesis

```{r}
tibble(
  Year = c(rep("2021-22", 4), rep("2020-21", 3), rep("2019-20", 3), rep("2016-17", 2), "2015-16", rep("2014-15", 2), rep("2013-14", 3), "2012-13"),
  Name = c("Raika Bourmand", "Armin Sariaslani", "Katharine Douglas", "Thinzar Soe", "Julianna Marfisi", "Matthew Tobis", "Andrew Poskus", "Sherry Feldman", "Olena Leschyshen", "Noura Balbaa", "Lauren Smail*", "Zachary Yantha*", "Michelle Nguyen*", "Victora Smith*", "Anna Head*", "Bethany Cseke*", "Dylan Klawitter*", "Codie Primeau*", "Helen Chong*"),
  Program = c("Kinesiology", rep("Life Sciences", 3), rep("Kinesiology", 3), "Life Sciences", rep("Kinesiology", 2), "Psychology", rep("Human Kinetics", 8)),
  Level = c(rep("IV", 19)),
  Institution = c(rep("McMaster University", 10), "Queen's University", rep("University of Ottawa", 8)),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  footnote(
    footnote_as_chunk = T,
    general_title = " ",
    general = "\\\\tiny *Denotes co-supervision",
    escape = F
  ) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 1, width = '1.5cm') #%>%
  #column_spec(column = 2:4, width = "3.5cm")
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

\newpage

# Administrative Responsibilities

```{r}
tibble(
  Years = c("2019-2021", "2019-20", "2018-20", "2017-Present", "2012-13"),
  Institution = c(rep("McMaster University", 4), "University of Ottawa"),
  Name = c("Department of Kinesiology Awards Committee (Undergraduate and Graduate),
Member", "Faculty of Science Awards Committee, Member", "Department of Kinesiology Undergraduate Curriculum and Policy", "Department of Kinesiology Graduate Curriculum and Policy", "CUPE 2626 Human Kinetics Union Steward"),
  #English = cell_spec(c("C2","C1","C2","C2"), 'latex', color = '#009acd'), # #009acd
  #French = cell_spec(c("B2","B2","B2","B2"), 'latex', color = '#009acd'), # #4cb8dc
) %>%
  kbl(format = "latex", booktabs = TRUE, align = 'l', escape = F, longtable = TRUE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), position = "left", full_width = F, font_size = 9, latex_options = c("hold_position", "repeat_header")) %>%
  row_spec(row = 0, bold = TRUE) %>% 
  column_spec(column = 3, width = '15cm')
  # add_header_above(' ', line = F) %>%
  # row_spec(0:4, extra_latex_after = "\\arrayrulecolor{white}") 
```

# Lifetime Publications

^+^Denotes trainee

## Current preprints

[2]. ^+^McKay B, **Carter MJ**. Data irregularities across six implicit learning articles: Comments on Lola, Giatis, Pérez-Turpin, and Tzetzis (2021), Lola and Tzetzis (2021), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010). *PsyArXiv*. doi: [https://doi.org/10.31234/osf.io/n8mab](https://doi.org/10.31234/osf.io/n8mab)

[1]. de Brouwer AJ, **Carter MJ**, ^+^Smail, LC, Wolpert DM, Gallivan JP, Flanagan JR. Gaze behaviour reveals flexible encoding of competing reach goals under conditions of target uncertainty. *BioRxiv*. doi: [10.31234/osf.io/s34fg](https://doi.org/10.31234/osf.io/s34fg)

\medskip

## Peer-reviewed journal articles

[24.] ^+^St. Germain L, ^+^Williams A, ^+^Balbaa N, ^+^Poskus A, ^+^Leshchyshen O, Lohse KR, **Carter MJ**. (in press). Increased perceptions of autonomy through choice fail to enhance motor skill retention. *Journal of Experimental Psychology: Human Perception and Performance*.

[23.] ^+^McKay B, Yantha ZD, Hussien J, **Carter MJ**, & Ste-Marie DM. (in press). Meta-analytic findings in the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value. *Meta-Psychology*.

[22.] ^+^McKay B, Hussien J, **Carter MJ**, Yantha Z, & Ste-Marie DM. (2021). Expecting to teach a novel golf putting task did not enhance retention performance: A replication attempt of Daou and colleagues. *Communications in Kinesiology*, 1: 1-21.

[21]. Barros JAC, ^+^Yantha ZD, **Carter MJ**, Hussein J, Ste-Marie DM (2019). Examining the impact of error estimation on the effects of self-controlled feedback. *Human Movement Science*, 63: 182–198.

[20]. **Carter MJ**, ^+^Smith V, Carlsen AN, Ste-Marie DM (2018). Anodal transcranial direct current stimulation over the primary motor cortex does not enhance the learning benefits of self-controlled feedback schedules. *Psychological Research*, 82: 496–506.

[19]. **Carter MJ**, Ste-Marie DM (2017). Not all choices are created equal: Task-relevant choices enhance motor learning compared to task-irrelevant choices. *Psychonomic Bulletin & Review*, 24:1879–1888.

[18]. Maslovat D, **Carter MJ**, Carlsen AN (2017). Response preparation and execution during intentional bimanual pattern switching. *Journal of Neurophysiology*, 118: 1720–1731.

[17]. **Carter MJ**, Ste-Marie DM (2017). An interpolated activity during the knowledge-of-results delay interval eliminates the learning advantages of self-controlled feedback schedules. *Psychological Research*, 81: 399–406.

[16]. **Carter MJ**, Maslovat D, Carlsen AN (2017). Intentional switches between coordination patterns are faster following anodal-tDCS applied over the supplementary motor area. *Brain Stimulation*, 10:162-164.

[15]. Ste-Marie DM, **Carter MJ**, Law B, Vertes K, ^+^Smith V (2016). Self-controlled learning benefits: Exploring contributions of self-efficacy and intrinsic motivation via path analysis. *Journal of Sport Sciences*, 34: 1650–1656.

[14]. **Carter MJ**, Rathwell S, Ste-Marie DM (2016). Motor skill retention is modulated by strategy choice during self-controlled knowledge of results schedules. *Journal of Motor Learning & Development*, 4: 100-115.

[13]. Patterson JT, Hart A, Hansen S, **Carter MJ**, Ditor D (2016). Measuring investment in learning: Can electrocardiogram provide an indication of cognitive effort during learning?. *Perceptual & Motor Skills*, 122: 375–394.

[12]. **Carter MJ**, ^+^Smith V, Ste-Marie DM (2016). Judgments of learning are significantly higher following feedback on relatively good versus relatively poor trials despite no actual learning differences. *Human Movement Science*, 45: 63–70.

[11]. Martini R, **Carter MJ**, ^+^Yoxon E, Cumming J, Ste-Marie DM (2016). Development and validation of the Movement Imagery Questionnaire for Children (MIQ-C). *Psychology of Sport & Exercise*, 22:190–201.

[10]. Maslovat D, Drummond NM, **Carter MJ**, Carlsen AN (2015). Startle activation is additive with voluntary cortical activation irrespective of stimulus modality. *Neuroscience Letters*, 606: 151–155.

[9]. Maslovat D, Drummond NM, **Carter MJ**, Carlsen AN (2015). Reduced motor preparation during dual-task performance: Evidence from startle. *Experimental Brain Research*, 233: 2673–2683.

[8]. **Carter MJ**, Maslovat D, Carlsen AN (2015). Anodal transcranial direct current stimulation applied over the supplementary motor area delays spontaneous antiphase-to-in-phase transitions. *Journal of Neurophysiology*, 133: 780–785.

[7]. **Carter MJ**, Carlsen AN, Ste-Marie DM (2014).Self-controlled feedback is effective if it is based on
the learner’s performance: A replication and extension of Chiviacowsky and Wulf (2005). *Frontiers in Psychology*, 5: Article 1325.

[6]. Maslovat D, **Carter MJ**, Kennefick M, Carlsen AN (2014). Startle neural activity is additive with normal cortical initiation-related activation. *Neuroscience Letters*, 558: 164–168.

[5]. Bajema MC, MacKinnon CD, **Carter MJ**, Kennefick M, Perlmutter S, Carlsen AN (2013). Pause time alters the preparation of two-component movements. *Experimental Brain Research*, 231: 85–96.

[4]. Patterson JT, **Carter MJ**, Hansen S (2013). Self-controlled KR schedules: Does repetition order matter? *Human Movement Science*, 31: 1459–1472.

[3]. **Carter MJ**, Patterson JT (2012). Self-controlled knowledge of results: Age-related differences in motor learning, strategies, and error detection. *Human Movement Science*, 31: 1459–1472.

[2]. Patterson JT, **Carter MJ**, Sanli E (2011). Decreasing the proportion of self-control trials during the acquisition period does not compromise the learning advantages in a self-controlled context. *Research Quarterly for Exercise & Sport*, 82: 624–633.

[1]. Patterson JT, **Carter MJ** (2010). Learner regulated knowledge of results during the acquisition of multiple timing goals. *Human Movement Science*, 29: 214–227.

\medskip
## Book chapters

[1]. Ste-Marie DM, **Carter MJ**, ^+^Yantha ZD (2019). Self-controlled learning: Current findings, theoretical perspectives, and future directions. In N Hodges & AM Williams (eds.) Chapter 7, *Skill acquisition in sport: Research, theory, and practice*, 3rd Edition.


# Talks

[8]. Open and reproducible research in a productivity demanding academic world. Motor Learning and Control Online Research Seminar Series, *North American Society for Psychology of Sport & Physical Activity*. Invited team talk with Drs. Diane Ste-Marie, Keith Lohse, and Matthew Miller, Nov 2020.

[7]. Motor learning and self-controlled practice conditions: What we know after 25 years of research. Distinguished lecture series, *Auburn University*. Invited, **Postponed due to Covid-19**.

[6]. Embracing uncertainty and learning to learn. Neuroscience Tutorial, *McMaster University*. Invited, Jan 2019.

[5]. Self-controlled feedback and error estimation. Symposium on "Errors make you better: Behavioural, theoretical, and neurophysiological determinates of error processing in motor learning", *Canadian Society for Psychomotor Learning & Sport Psychology*. Invited, Oct 2018.

[4]. Decision-making for action control and learning. Kinesiology Seminar Series, *McMaster University*. Invited, Sept 2017.

[3]. Cognition and motor skill learning: Insights from learner-controlled protocols. Centre for Neuroscience Studies Seminar Series, *Queen’s University*. Invited, May 2016.

[2]. Self-controlled feedback and motor learning. Franklin Henry Young Scientist Award Presentation, *Canadian Society for Psychomotor Learning & Sport Psychology*. Invited, Oct 2014.

[1]. Cognitive processes underlying the learning advantages of self-controlled feedback schedules. Biokinesiology & Physical Therapy Seminar Series, *University of Southern California*. Invited, March 2015.

# Conference Presentations
**Presenting author(s)**; ^+^Denotes trainee

## 2021
[43.] Lokesh R Calalo J, Roth A, Carter MJ, Cashaback JGA. Rapid decision-making during competitive human-human sensorimotor interactions. Talk given at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Virtual Conference due to Covid-19.

[42.] Roth A, Lokesh R, Calalo J, Carter MJ, Cashaback JGA. The influence of reward feedback and error feedback on sensorimotor exploration. Talk given at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Virtual Conference due to Covid-19.

[41.] **^+^St. Germain L**, ^+^McKay B, ^+^Williams A, ^+^Leshchyshen O, ^+^Poskus A, ^+^Feldman S, Cashaback JGA, Carter MJ. Binary feedback prevents a self-controlled learning advantage. Talk given at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Virtual Conference due to Covid-19.

[40]. **^+^Marfisi J**, ^+^St. Germain L, Carter MJ. The persistence of inappropriate outcome variables in motor learning experiments: A follow-up to Fischman (2015). Poster presented at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Virtual Conference due to Covid-19.

[39]. **Hussien J**, McKay B, Carter MJ, Yantha Z, Brooks H, Hassin J, Turenne M, Ste-Marie DM. Failure to demonstrate an ‘expecting to teach’ benefit: A replication and extension experiment. Talk given at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Virtual Conference due to Covid-19.

\medskip
## 2020
[38]. **^+^St. Germain L**, ^+^Williams A, ^+^Poskus A, ^+^Balbaa N, ^+^Leshchyshen O, Lohse KR, Carter MJ. Self-controlled learning: Making a yoked group explicitly aware of being denied choice. Talk given at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Virtual Conference due to Covid-19.

\medskip
## 2019
[37]. **^+^St. Germain L**, ^+^Leshchyshen O, ^+^Williams A, Carter MJ. Manipulating the characteristics of self-controlled feedback schedules. Talk given at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Vancouver BC, Canada.

[36]. **^+^Williams A**, **^+^St. Germain L**, ^+^Leshchyshen O, Carter MJ. Error estimation abilities and self-
controlled feedback schedules. Poster presented at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Vancouver BC, Canada.

[35]. **^+^St. Germain L**, **^+^Leshchyshen O**, Carter MJ. Assessing the evidential value of incidental choices
for motor learning. Poster presented at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Baltimore MD, United States.

[34]. **Yantha ZD**, McKay B, Carter MJ, Ste-Marie DM. The effects of choice on motor skill learning: A meta-analysis of self-controlled research findings. Poster presented at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Baltimore MD, United States.

\medskip
## 2018
[33]. ^+^Zahir F, **^+^St. Germain L**, **Carter MJ**. Inconvenient findings for the "OPTIMAL" theory of motor learning. Poster presented at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Toronto ON, Canada.

<!-- \medskip -->
\newpage
## 2017
[32]. **Gale D**, Carter MJ, Wolpert DM, Gallivan JP, Flanagan JR. Dynamic motor encoding of targets in multiple target tracking. Poster presented at the Annual Meeting of the *Society for Neuroscience*; Washington DC, United States.

[31]. **Carter MJ**, de Brouwer AJ, ^+^Smail L, Wolpert DM, Gallivan JP, Flanagan JR. Gaze behaviour reveals the specification of competiting reach movements under conditions of target uncertainty. Talk given at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; St. John’s NF, Canada.

[30]. **^+^Yantha ZD**, Carter MJ, Hussein J, Cotnam HP, Ste-Marie DM. Using error estimation to better understand the advantages of self-controlled practice. Talk given at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; St. John’s NF, Canada.

[29]. **Carter MJ**, de Brouwer AJ, ^+^Smail L, Wolpert DM, Gallivan JP, Flanagan JR. Gaze behaviour reveals the specification of competing reach movements. Poster presented at the Annual Meeting of the *Society for the Neural Control of Movement*; Dublin, Ireland.

## 2016
[28]. ^+^Yantha ZD, **Carter MJ**, Ste-Marie DM. Task-relevant and task-irrelevant choices differentially impact error estimation and motor learning. Talk given at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Waterloo ON, Canada.

[27]. **Carter MJ**, ^+^Elnakouri A, ^+^Yantha ZD, Ste-Marie DM. Not all choices are created equal: The differential impact of task-relevant and task-irrelevant choices on motor learning. Poster presented at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Montreal QC, Canada.
 
[26]. **Carter MJ**, Maslovat D, Carlsen AN. A startling acoustic stimulus suggests advance preparation of intentional bimanual switches. Poster presented at the Annual Meeting of the *Society for the Neural Control of Movement*; Montego Bay, Jamaica.

\medskip
## 2015
[25]. **Ste-Marie DM**, Carter MJ, Law B, *Smith V, Vertes KA. Self-controlled learning benefits: Exploring contributions of self-efficacy and intrinsic motivation via path analysis. Poster presented at the Annual Meeting of the *European Congress of Sport Psychology*; Bern, Switzerland.

[24]. **Carter MJ**, Carlsen AN, ^+^Smith V, Ste-Marie DM. Anodal transcranial direct current stimulation applied over the primary motor cortex does not enhance the learning benefits of self-controlled KR schedules. Poster presented at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Edmonton AB, Canada.

[23]. **Carter MJ**, ^+^Head CA, Puveendran P, Ste-Marie DM. Eliminating the learning benefits of self-controlled knowledge of results (KR) schedules: The improtance of information processing activities during the KR-delay interval. Talk given at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Portland OR, United States.

[22]. **Carter MJ**, Carlsen AN, Ste-Marie DM. Self-controlled feedback is effective if it is based on the learner’s performance: A replicaiton and extension of Chiviacowsky & Wulf (2005). Talk given at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Portland OR, United States.

[21]. **Carter MJ**, Maslovat D, Nguyen M, Carlsen AN. The learning of a 90-degree relative phase bimanual coordination pattern: A transcranial direct current stimulation investigation. Poster presented at the Annual Meeting of the *Society for the Neural Control of Movement*; Charleston SC, United States.

\medskip
## 2014
[20]. **McKay B**, **Carter MJ**, Rathwell S, Ste-Marie DM.The learning benefits of self-controlled feedback schedules are modulated by strategy choice: A mixed-methods approach. Poster presented at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; London ON, Canada.

[19]. **Drummond NM**, Maslovat D, Carter MJ, Chiucchi A, Carlsen AN. Startle activation is additive with voluntary cortical activation irrespective of stimulus modality. Poster presented at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; London ON, Canada.

[18]. **Carter MJ**, ^+^Klawitter D, Carlsen AN, Ste-Marie DM. The option of receiving knowledge of results following performance leads to increased motor learning. Talk given at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Minneapolis MN, United States.

[17]. **Carter MJ**, **^+^Smith V**, Carlsen AN, Ste-Marie DM. Awareness of "good" versus "poor" feedback content does not mitigate illusions of competency. Poster presented at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Minneapolis MN, United States.

[16]. **McKay B**, Carter MJ, Ste-Marie DM. Self-controlled learning: A meta-analysis. Poster presented at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Minneapolis MN, United States.

[15]. **Carter MJ**, ^+^Cseke B, Drummond NM, Carlsen AN. Intentional phase transitions in bimanual coordination following tDCS. Poster presented at the Annual Meeting of the *Society for the Neural Control of Movement*; Amsterdam, The Netherlands.

[14]. **Drummond NM**, Scantland-Lebel I, Carter MJ, Maslovat D, Carlsen AN. Startle reveals motor preparatory state associated with differential attentional demands. Poster presented at the Annual Meeting of the *Society for the Neural Control of Movement*; Amsterdam, The Netherlands.

\medskip
## 2013
[13]. **Carter MJ**, Drummond NM, Carlsen AN. Anodal tDCS decreases mean relative phase error during anti-phase movements. Poster presented at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Kelowna BC, Canada.

[12]. **Ste-Marie DM**, Law B, **Carter MJ**, Westlund N, Divine A, Martini R. Group versus individual administration of Movement Imagery Questionnaire for Children yields different movement imagery scores. Poster presented at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Kelowna BC, Canada.

[11]. Vertes KA, **Carter MJ**, ^+^Smith V, Ste-Marie DM. Self-controlled video feedback is effective for learning when children adopt higher viewing frequencies. Talk given at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; New Orleans LA, United States.

[10]. **Carter MJ**, ^+^Yoxon E, Ste-Marie DM, Cumming J, Martini R. The validation of a movement imagery questionnaire for children (MIQ-C). Poster presented at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; New Orleans LA, United States.

[9]. **Carter MJ**, Maslovat D, Drummond NM, Kennefick M, Carlsen AN. Startle neural activity is additive with normal cortical initiation-related activation. Poster presented at the Annual Meeting of the *Society for the Neural Control of Movement*; San Juan, Puerto Rico.

[8]. **Drummond NM**, Hayduk-Costa G, Carter MJ, Carlsen AN. Bi-hemispheric tDCS over motor cortex does not influence free choice. Poster presented at the Annual Meeting of the *Society for the Neural Control of Movement*; San Juan, Puerto Rico.

\medskip
## 2012
[7]. **Carter MJ**, Drummond NM, Ste-Marie DM, Carlsen AN. Providing knowledge of results based on an absolute performance bandwidth results in illusions of competency. Talk given at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Halifax NS, Canada.

[6]. **Hayduk-Costa G**, Drummond NM, Carter MJ, Carlsen AN. Turbocharging the "go"-horse: Anodal tDCS results in early response initiation in an anticipation timing task. Talk given at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Halifax NS, Canada.

[5]. **Kennefick M**, Carter MJ, Bajema MC, Carlsen AN. Dwell time mediates the preparation of single versus multiple component movements. Poster at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Halifax NS, Canada.

\medskip
## 2011
[4]. **Carter MJ**, Patterson JT. Self-controlled practice: Learning differences between younger and older adults. Poster presented at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Winnipeg MB, Canada.

\medskip
## 2010
[3]. **Carter MJ**, Patterson JT. Self-controlled KR: Does it facilitate an internal representation of a spatial motor task?. Poster presented at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Ottawa ON, Canada.

[2]. **Carter MJ**, Patterson JT, Hansen S. Learner-controlled KR: Does repetition order matter?. Poster presented at the Annual Meeting of the *North American Society for Psychology of Sport & Physical Activity*; Tuscan AZ, United States.

\medskip
## 2009
[1]. **Carter MJ**, Patterson JT. Manipulating the structure of a learner-controlled KR practice context: Do the learning advantages persist?. Poster presented at the Annual Meeting of the *Canadian Society for Psychomotor Learning & Sport Psychology*; Toronto ON, Canada.
